Case for Support

### 2021-11-16 application/backgroundToTheResource.tex
Added caption to wrapfigure

\setlength{\columnsep}{1em}
\begin{wrapfigure}{r}{0.5\textwidth}
  \includegraphics[width=0.5\columnwidth,viewport=65 50 500 800,clip]{figures/bonsai.pdf}
  \label{fig:bonsai}
\end{wrapfigure}
\stepcounter{figure}

>>>>

\setlength{\columnsep}{1em}
\begin{wrapfigure}{R}{0.5\textwidth}
  % \includegraphics[width=0.5\columnwidth,viewport=65 50 500 800,clip]{figures/bonsai_noCaption.pdf}
    \includegraphics[width=0.48\textwidth]{figures/roadmap-bbsrc_noCaption.png}

  \caption{Bonsai development timmeline and community adoption. (A) Timeline of
    milestones and landmark package releases. (B) Example neuroscience
    experiments developed in Bonsai over the years. (C) Example Bonsai workflow
    for tracking the positioon of objects in a video. (D) Worldwide
    distribution of visitors to the bonsai-rx.org website. (E)
    Number of downloads for each Bonsai version. (F) Cumulative number of
    registered forum users, citations of the main publication, and number of
    training events, by year (bottom panels), versus release and development
    cycle (top panel), measured in commits to main repository.}
  \label{fig:bonsai}

\end{wrapfigure}
% \stepcounter{figure}
